Job Demands-Resources Model Components through the Lens of O*NET Classifications

### 2023-03-04 Submission.tex
updating results

The mean resource to challenge correlation was \_\_\_\_\_\_\_\_\_\_. The mean resource to hindrance correlation was \_\_\_\_\_\_\_\_\_\_. Finally, the mean challenge to hindrance correlation was \_\_\_\_\_\_\_\_\_\_\_\_. These were expected to be moderate in size, but smaller than within the same category. In sum, Challenge and hindrance demands demonstrated smaller relationships, but mostly negative. Challenge and resource are strongly and positively related. These results provide support for H2, suggesting that there is overlap in how employees perceive job characteristics - particularly regarding what is perceived as a \emph{resource} being also perceived as a \emph{challenge}. Stated another way, job characteristics are not uniquely categorized as a resource or as a demand.

>>>>

The mean resource to challenge correlations within the same dimension ranged from .62 to .66, \emph{M} = .64, \emph{SD} = .02). The correlations between resources and challenges across dimensions ranged from .08 to .50, \emph{M} = .32, \emph{SD} = .12. The mean resource to hindrance correlations within the same dimension ranged from -.16 to -.30, \emph{M} = -.24, \emph{SD} = .05). The correlations between resources and hindrances across dimensions ranged from .05 to -.27, \emph{M} = -.14, \emph{SD} = .08. The mean challenge to hindrance correlations within the same dimension ranged from -.04 to -.27, \emph{M} = -.21, \emph{SD} = .08). The correlations between challenges to hindrances across dimensions ranged from .12 to -.26, \emph{M} = -.11, \emph{SD} = .09. Correlations were larger when what was being rated was the same type of characteristic. In sum, Challenge and hindrance demands demonstrated smaller relationships, but mostly negative. Challenge and resource are strongly and positively related. These results provide support for H2, suggesting that there is overlap in how employees perceive job characteristics - particularly regarding what is perceived as a \emph{resource} being also perceived as a \emph{challenge}. Stated another way, job characteristics are not uniquely categorized as a resource or as a demand.
